Manuscript 1 code

### 2024-09-12 manuscript_1_code.Rmd
Made figures 3f and 4f

```{r synchrony cover mod}
synch_cov_mod <- glmmTMB(cover_mean ~ synchrony*habitat + (1|site), family = beta_family(), data = diversity_stability_synchrony)
summary(synch_cov_mod)

emtrends(synch_cov_mod, pairwise ~ habitat, var = "synchrony") # forereef 17 distinct from all other habitats
```

```{r synch cov mod setup}
synch_cov_emm <- emmip(synch_cov_mod,
                        habitat ~ synchrony,
                        at = list(synchrony = seq(0,1,0.01)), plotit = F, CIs = T)

@@

>>>>

```{r synchrony cover mod}
synch_cov_mod <- glmmTMB(cover_mean ~ synchrony*habitat + (1|site), family = beta_family(), data = diversity_stability_synchrony)
summary(synch_cov_mod)
hist(residuals(synch_cov_mod)) # slight skew
plot(residuals(synch_cov_mod) ~ fitted(synch_cov_mod)) # same issues as always
emtrends(synch_cov_mod, pairwise ~ habitat, var = "synchrony") # forereef 17 distinct from all other habitats
```

```{r synch cov plot setup}
synch_cov_emm <- emmip(synch_cov_mod,
                        habitat ~ synchrony,
                        at = list(synchrony = seq(0,1,0.01)), plotit = F, CIs = T)

@@

## figure 4f

```{r synchrony staability mod site}
synch_stab_mod_site <- glmmTMB(cover_stability ~ synchrony*habitat, family = Gamma("log"), data = diversity_stability_synchrony_site)
summary(synch_stab_mod_site)
hist(residuals(synch_stab_mod_site)) # almost uniform
plot(residuals(synch_stab_mod_site) ~ fitted(synch_stab_mod_site)) # same issue as always
r.squaredGLMM(synch_stab_mod_site) # 0.678
emtrends(synch_stab_mod_site, pairwise ~ habitat, var = "synchrony") # fringing and backreef are different from forereef 17
```

```{r figure 4f setup}

synch_stab_emm_site <- emmip(synch_stab_mod_site,
                        habitat ~ synchrony,
                        at = list(synchrony = seq(0,1,0.01)), plotit = F, CIs = T)

filtered_synch_stab_effects_site <- synch_stab_emm_site %>%
  left_join(dss_ranges_site, by = c("habitat")) %>%
  filter(synchrony >= min_synchrony & synchrony <= max_synchrony)

## plot figure 4f

```{r figure 4c}
(figure_4f <- 
  ggplot() +
  geom_point(data = diversity_stability_synchrony_site,
             aes(x = synchrony, y = cover_stability, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_synch_stab_effects_site, aes(x = synchrony, y = exp(yvar), colour = habitat)) +
  geom_ribbon(data = filtered_synch_stab_effects_site, aes(x = synchrony, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(x = "Synchrony", y = "Stability\n", main = "4f.") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18),
        plot.title = element_text(size=18),
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_rect(fill = "white"),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )
ggsave(filename = "output/figure_4f.png", figure_4f, height = 10, width = 14)
```

# figure 3f

## model

```{r synchrony cover mod}
synch_cov_mod_site <- glmmTMB(cover_mean ~ synchrony*habitat, family = beta_family(), data = diversity_stability_synchrony_site)
summary(synch_cov_mod_site)
hist(residuals(synch_cov_mod_site)) # slight skew
plot(residuals(synch_cov_mod_site) ~ fitted(synch_cov_mod_site)) # looks fine
emtrends(synch_cov_mod_site, pairwise ~ habitat, var = "synchrony") # forereef 17 different from backreef
```

```{r synch cov site plot setup}
synch_cov_emm_site<- emmip(synch_cov_mod_site,
                        habitat ~ synchrony,
                        at = list(synchrony = seq(0,1,0.01)), plotit = F, CIs = T)

filtered_synch_cov_effects_site <- synch_cov_emm_site %>%
  left_join(dss_ranges_site, by = c("habitat")) %>%
  filter(synchrony >= min_synchrony & synchrony <= max_synchrony)
```

## plot figure 3f

```{r synchrony cover plot site}
(figure_3f <- 
  ggplot() +
  geom_point(data = diversity_stability_synchrony_site,
             aes(x = synchrony, y = cover_mean, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_synch_cov_effects_site, aes(x = synchrony, y = exp(yvar), colour = habitat)) +
  geom_ribbon(data = filtered_synch_cov_effects_site, aes(x = synchrony, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(x = "Synchrony", y = "Cover\n", title = "3f.") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        plot.title = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_rect(fill = "white"),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

ggsave(filename = "output/figure_3f.png", figure_3f, height = 10, width = 14)
```
